Composable Algebra with Dependencies

### 2015-04-18 dAlg/mrm.tex
Abstract & Introduction (for FYP report)

\authorinfo{Bruno C. d. S. Oliveira}
           {University of Hong Kong}
           {bruno@cs.hku.hk}
\authorinfo{Shin-Cheng Mu}
           {Academia Sinica}
           {scm@iis.sinica.edu.tw}
\authorinfo{Shu-Hung You}
           {National Taiwan University}
           {suhorngcsie@gmail.com}
\maketitle

@@

@@

Apart from functors and F-Algebras, there are other ways to represent and evaluate
the DSL of parallel prefix circuits. In this section, we will show two other 
representations, and how they can be used to allow dependent interpretations.

@@

\bibitem{gibbons14}
  Gibbons, Jeremy and Wu, Nicolas.
  Folding Domain-Specific Languages: Deep and Shallow Embeddings.
  2014.

\bibitem{sheard04}
  Sheard, Tim and Pasalic, Emir.
  Two-level types and parameterized modules.
  \textit{Journal of Functional Programming}.
  14(5):547-587, September 2014.

>>>>

\authorinfo{Draft}
           {}
           {}

\maketitle

@@

This paper presents composable algebra with dependencies: a new approach to compose 
algebras together to allow dependent interpretations with {\em fold}. 
For a given datatype represented by two-evel-types\cite{sheard04}, if one of its 
interpretations depends on a second interpretation, we compose the algebra correponding 
to this interpretation with the algebra corresponding to the second one, and use the 
composed algebra with {\em fold} to evaluate the expression.

@@

Apart from {\em two-level-types}, there are other ways to represent and evaluate
the DSL of parallel prefix circuits. In this section, we will show two other 
representations, and how they can be used to allow dependent interpretations.

@@

\bibitem{sheard04}
  Sheard, Tim and Pasalic, Emir.
  Two-level types and parameterized modules.
  \emph{Journal of Functional Programming}.
  14(5):547-587, September 2014.

\bibitem{gibbons14}
  Gibbons, Jeremy and Wu, Nicolas.
  Folding Domain-Specific Languages: Deep and Shallow Embeddings.
  \emph{International Conference on Functional Programming}.
  2014.
